Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-12-05 paper/main.tex
move table to front and discuss it

@@

\begin{table}[H]
    \centering
    \begin{tabular}{l c c c c c c}
        \toprule
        % \multicolumn{6}{Growth Rates}\\
        Method & Cell $0$ & Cell $1$ & Cell $2$ & Cell $3$ & Cell $4$ & Cell $5$\\
        \midrule
        Fit   & 0.001405 & 0.001080 & 0.002317 & 0.001512 & 0.002048 & 0.001672\\
        \ac{abm} Direct & 0.001152 & 0.001410 & 0.001876 & 0.001683 & 0.003610 & 0.001520\\
        \ac{abm} Imaging\\
        % 0.0014057073 & 0.0010807540 & 0.0023177727 & 0.0015120675 & 0.0020488179 & 0.0016726263\\
        % direct & 0.0009785162 & 0.0012641432 & 0.0021701728 & 0.0015695889 & 0.0036255661 & 0.0018419186\\
        \bottomrule
    \end{tabular}
    \caption{TODO Update and explain these values. And also add units!}
\end{table}

>>>>

\textbf{TODO write text to compare the numerical values. This needs updated input from results.}
Table~\ref{tab:comparison-growth-rates} shows the obtained values for the growth rates via the
different techniques.
Although numerical values differ between the individual settings, each estimation technique was able
to capture the same trends.
Cell $0,1,3$ tend to be the fastest growing cells while $2,4,5$ are slower.
Furthermore, we can see that daughter cells tend to grow quicker compared to mother cells,
indicating the their parents were still adapting to the new environment.

\begin{table}[H]
    \centering
    \begin{tabular}{l c c c c c c}
        \multicolumn{4}{l}{\textbf{Growth Parameters for different Methods}}\\
        \toprule
        % \multicolumn{6}{Growth Rates}\\
        Method & Cell $0$ & Cell $1$ & Cell $2$ & Cell $3$ & Cell $4$ & Cell $5$\\
        \midrule
        Fit             & 0.00703 & 0.00540 & 0.01159 & 0.00756 & 0.01024 & 0.00836\\
        \ac{abm} Direct & 0.00671 & 0.00746 & 0.01138 & 0.00848 & 0.02005 & 0.00952\\
        \ac{abm} Imaging& 0.00104 & 0.00146 & 0.00206 & 0.00286 & 0.00190 & 0.00171\\
        & \textbf{Daughters}\\
        \midrule
        & Cell $0$ & Cell $1$ & Cell $2$ & Cell $3$ & Cell $4$ & Cell $5$\\
        & 0.00240 & 0.00494 & 0.00096 & 0.00363\\
        & 0.00490 & 0.00226 & 0.00448 & 0.00048\\
        % 0.0014057073 & 0.0010807540 & 0.0023177727 & 0.0015120675 & 0.0020488179 & 0.0016726263\\
        % direct & 0.0009785162 & 0.0012641432 & 0.0021701728 & 0.0015695889 & 0.0036255661 & 0.0018419186\\
        \bottomrule
    \end{tabular}
    \caption{
        \textbf{TODO maybe report uncertainties?}
        \textbf{TODO Update and explain these values. And also add units!}\\
        \textbf{TODO FIX NUMERICAL VALUES}\\
        \textbf{TODO check ordering}
    }
    \label{tab:comparison-growth-rates}
\end{table}

@@
